Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-18 Papers/ms.tex
New simdata figures

We executed the code to generate 3,000 samples from the ``mixture of
constrained priors'' distribution of DNest. Our thinning factor was $10^5$,
so $3 \times 10^8$ MCMC iterations were actually performed, taking approximately
30 hours on a PC purchased new in 2012. After resampling these samples to
reflect the posterior distribution, we were left with 318
(equally weighted) posterior samples.

@@

The estimated marginal likelihood of our model
(averaged over all parameters including $N_{\rm lens}$ and $N_{\rm src}$)
is
$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14249$, and
the information (Kullback-Leibler divergence from the prior to the posterior)
is $\mathcal{H} \approx 100$ nats. The information represents the degree of
compression of the posterior distribution with respect to the prior, and can
be interpreted quite literally as how much was learned about the parameters from
the data. It is also straightforward to estimate from Nested Sampling
\citep{skilling}. Its definition is:
\begin{eqnarray}
\mathcal{H} = \int p(\boldsymbol{\theta} | \boldsymbol{D})
\ln\left[\frac{p(\boldsymbol{\theta} | \boldsymbol{D})}{p(\boldsymbol{\theta})}\right]
\, d\boldsymbol{\theta}
\end{eqnarray}
and we can build intuition about its meaning based on some simple examples. One
such example is a uniform prior over a volume $V_0$ and a posterior which is
uniform over a smaller volume $V_1$ contained within $V_0$. In this case
$\mathcal{H} = \ln(V_0/V_1)$ nats. Therefore, a value of $\mathcal{H}=100$ nats
implies the posterior distribution occupies roughly $e^{-100}$ of the prior
volume.

>>>>

We executed the code to generate 5,000 samples from the ``mixture of
constrained priors'' distribution of DNest. Our thinning factor was $10^5$,
so $5 \times 10^8$ MCMC iterations were actually performed, taking approximately
48 hours on a PC purchased new in 2012. After resampling these samples to
reflect the posterior distribution, we were left with 537
(equally weighted) posterior samples.

@@

The estimated marginal likelihood of our model
(averaged over all parameters including $N_{\rm lens}$ and $N_{\rm src}$)
is
$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -14248$, and
the information (Kullback-Leibler divergence from the prior to the posterior)
is $\mathcal{H} \approx 99$ nats. The information represents the degree of
compression of the posterior distribution with respect to the prior, and can
be interpreted quite literally as how much was learned about the parameters from
the data. It is also straightforward to estimate from Nested Sampling
\citep{skilling}. Its definition is:
\begin{eqnarray}
\mathcal{H} = \int p(\boldsymbol{\theta} | \boldsymbol{D})
\ln\left[\frac{p(\boldsymbol{\theta} | \boldsymbol{D})}{p(\boldsymbol{\theta})}\right]
\, d\boldsymbol{\theta}
\end{eqnarray}
and we can build intuition about its meaning based on some simple examples. One
such example is a uniform prior over a volume $V_0$ and a posterior which is
uniform over a smaller volume $V_1$ contained within $V_0$. In this case
$\mathcal{H} = \ln(V_0/V_1)$ nats. Therefore, a value of $\mathcal{H}=100$ nats
implies the posterior distribution occupies roughly $e^{-100}$ of the prior
volume.
